graphsim: An R package for simulating gene expression data from graph structures of biological pathways

### 2020-04-30 paper/paper.Rmd
Rmarkdown figure 4 #13

>>>>

```{r simulation_smad, fig.align='center', fig.show='hold', fig.width='1.0\\linewidth', fig.height='1.0\\linewidth', out.height='.415\\linewidth', out.width='.415\\linewidth', fig.retina=10, fig.margin = FALSE, fig.ncol = 2, fig.cap = '\\textbf{Simulating expression from a biological pathway graph structure}. The graph structure (a) of a known biological pathway, the TGF-$\\beta$ receptor signaling activates SMADs (R-HSA-2173789), was used to derive a relationship matrix (b), $\\Sigma$ matrix (c) and correlation structure (d) from the relative distances between the nodes. These values are coloured blue to red from $-1$ to $1$. This has been used to generate a simulated expression dataset of 100 samples (coloured blue to red from low to high) via sampling from the multivariate normal distribution. Here modules of genes with correlated expression can be clearly discerned.'}

#import graph from data
graph <- identity(TGFBeta_Smad_graph)

#generate parameters for inhibitions
state <- rep(1, length(E(graph)))
pathway <- get.edgelist(graph)
state[pathway[,1] %in% c("SMAD6", "SMAD7", "BAMBI", "SMURF1", "SMURF2", "UCHL5", "USP15", "UBB", "UBC", "PMEPA1", "PPP1CA", "PPP1CB", "PPP1CC", "PPP1R15A")] <- 2
state[is.na(state)] <- 1

plot_directed(graph, state=state, layout = layout.kamada.kawai,
              cex.node=3, cex.arrow=5, arrow_clip = 0.2,
              sub = expression(paste("(a) TFG-", Beta, " activates SMADs")), cex.sub = 1.5)
